---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# circ

`circ` is a small library that implements and tests the string operators, `lcirc` & `rcirc`. The purpose of this package is to showcase the reproducibility and good software hygeine promoted and easily used by the modern wave of R programming tools.

Some of the tools showcased by this package are:  

- `packrat`: Self-contained package management  
- `devtools`: Akin to `tidyverse`, but for easy R package development   
- `usethis`: Automated tasks such as README generation, test generation, and Travis setup  
- `testthat`: Unit testing   
- `covr`: Coverage testing, including an API for connection with [codecov.io]()  
- `roxygen2`: Automated documentation generation via commenting  

## Examples

```{r examples, eval = F}
str <- "statistics"

lcirc(str)
lcirc(str, 3)

rcirc(str, 4)

str %>% lcirc(14) %>% rcirc(31) %>% lcirc(17) 
```